Something something

### 2024-08-29 paper/ms.tex
Add one zone model res text

@@

\subsection{Time Dependence}\label{sec:timedep}

>>>>

\subsection{One-Zone Model}\label{ssec:onezone}

@@

We showed in Figure~\ref{fig:fig1} that a time-linear $\alpha$-enhancement of old stars (forming before $z=1.5$) led to the emergence of a strong chemical bimodality. This $\alpha$-enhancement is equivalent to saying that \alphaFe{} declines more rapdily with time at high-$z$. In Figure~\ref{fig:vice} we demonstrate an argument for why this steeper decline in \alphaFe{} might be absent in TNG.

We show in the upper panel the evolution of \MgFe{} of three one zone chemical evolution models which vary the star formation timescale. This timescale, $\tau_{\star}$, is the inverse of the star formation efficiency. A shorter star formation timescale leads to a more rapid reduction in \MgFe{}. In the shortest timescale model, $\tau_{\star}=0.5\,\Gyr$, \MgFe{} drops from $\sim0.45$ to $0.08\,\dex$ in $2\,\Gyr$. In comparison, the longest timescale model, $\tau_{\star}=5\,\Gyr$ only drops to $\sim0.2\dex$ in the same time.

The lower panel shows the negative of the time derivative of \MgFe{}. This panel shows the same behavior, with the slope of the $\tau_{\star}=0.5\,\Gyr$ model peaking at $-0.5\,\dex/\Gyr$ compared to the $5\,\Gyr$ model which peaks at $-0.25\,\dex/\Gyr$. After $1\,\Gyr$, the trend starts to reverse, with the longer star formation timescale models declining more rapidly, though at a much reduced rate ($\sim-0.1\,\dex/\Gyr$) than at the peak.
